A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-04-15 paper/main.tex
Frontmatter comments

\title{\textit{F1000Research} A studyforrest extension, an annotations of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description}
\titlenote{whatever titlenote here}

@@

@@

% new; not from haeusler2016annotation
Because naturalistic stimuli are multi-dimensional and their temporal structure
is (usually) unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. Nevertheless, theory-driven analyses like a general
linear model (GLM) are necessary to not just explain how but also when and why a
brain region is responding to a stimulus \citep{hamilton2018revolution}. Studies
using GLMs based on annotations of a stimulus' temporal structure have
elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.

>>>>

\title{A studyforrest extension, an annotation of words and phonemes in the German dubbed movie ``Forrest Gump'' and its audio-description}
%\titlenote{whatever titlenote here}

@@

\todo[inline]{The abstract should come now. It is needed to evaluate the
concept of the paper in the light of its content and vice versa.}

@@

% new; not from haeusler2016annotation
Because naturalistic stimuli are multi-dimensional and their temporal structure
is (usually) unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. Nevertheless, theory-driven\todo{model-based?, there is little theroy in GLM} analyses like a general
linear model (GLM) are necessary to not just explain how but also when and why a
brain region is responding to a stimulus \citep{hamilton2018revolution}. Studies
using GLMs based on annotations of a stimulus' temporal structure have
elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.
